---
title: "Team_Essay_3"
author: "Sahil, Ariel, Ilya, Lekha, Anthony, Trang"
date: "3/18/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Trang.

## Formula and Basics

Trang.

## Loading required R packages

```{r}
library("readxl")
library("tidyverse")
library("flexplot")
library("caret")
```


## Data description

Examples of data and problem: 

- Name: represents name of passenger
- PClass: represents the passenger class (1st, 2nd, 3rd)
- Age: represents age of the passenger in years (N/A if unknown)
- Sex: represents the sex of the passenger in terms of Male/Female
- Survived: represents survival status of passenger in terms of survived(1)/didn't survive(0)

```{r}
titanic <- read_excel("Titanic.xlsx")
titanic <- titanic[1:1313,]
index <- titanic$Age != "NA"
titanic <- titanic[index, ]
titanic$PClass = as.factor(titanic$PClass)
titanic$Sex = as.factor(titanic$Sex)
titanic$Survived = as.factor(titanic$Survived)
titanic$Age = as.factor(titanic$Age)
str(titanic)
```


## Visualization

Anthony needs to do the visualization.

## Analysis

This is the bi-variate dependency result.

```{r}
a = flexplot(Name~1, data = titanic)
b = flexplot(PClass~1, data = titanic)
c = flexplot(Age~1, data = titanic)
d = flexplot(Sex~1, data = titanic)
e = flexplot(Survived~1, data = titanic)
require(cowplot)
plot_grid(a, b, c, d, e, nrow=2)
```

This neat visualization shows us the number of people that are male/female, the number of people that survived, the number of people aged between ranges and the number of people belonging to 1st, 2nd and 3rd class respectively.

This is the multivariate dependency result.

```{r}
f = flexplot(Survived~Sex + Age + PClass, data = titanic, method="Binomial", se=F, jitter=c(0, 0.2)) 
plot_grid(f)
```


```{r}
f = plot(x = titanic$Age, y = titanic$Survived)
g = flexplot(Survived~Sex, data = titanic, method="Binomial", se=F, jitter=c(0, 0.2))
h = flexplot(Survived~PClass, data = titanic, method="Binomial", se=F, jitter=c(0, 0.2))
plot_grid(f, g, h)
```


## Computation and Model assessment

```{r}
model_2 <- glm(Survived~ PClass + Sex, data=titanic, family=binomial)
summary(model_2)
anova(model_2)
model_2_probs = predict(model_2, type="response")
model_2_predict <- rep("0", nrow(titanic))
model_2_predict[model_2_probs > .6] <- "1"
table(Predicted = model_2_predict, Reference = titanic$Survived)
```


First things first we construct our binomial model which relates whether the passenger survived to the passenger's boarding class and sex. When we look at the summary and      plots of this model, we see that not only are the predictors significant, but our residuals are quite close to our actual values. However, the AIC value is pretty high which can indicate that our model is not actually a good fit. Nonetheless, what matters is actually testing our model's predictive capabilities. We do this by calculating the 
probability of that someone on the titanic survived. Then, for any probability that is greater than 60% that the passenger survived, we predict that the passenger actually   did survive. Finally, we create a confusion matrix to see how many survived and deceased passengers we correctly predicted along with the passengers we incorrectly           predicted. Using this, we can calculate the overall accuracy of our predictive model that, when computed, gives us an accuracy of around 79%. 
## Interpretation and Model evaluation

We interpret the results given by the model as:
  + Sex and PClass are the 2 significant predictors, hence we make the model which includes only them.
  + Name and Age are the 2 insignificant predictors, hence we thought it was safe to remove them during model creation.
  + People who survived mostly belonged to the 1st and 3rd Class and were females.
  + Our model is not perfect since AIC can be much smaller than the current value. (AIC: 731.59)
  + The residual deviance also could have been lower, but this is due to more numeber of outliers. (Residual deviance:  723.59  on      752  degrees of freedom)
  
## Coefficients significance Prediction and Model accuracy

Ilya and Lekha

## Conclusion and Summary

Ilya and Lekha

## Reference

Ilya and Lekha
