---
title: "Team_Essay_3"
author: "Sahil, Ariel, Ilya, Lekha, Anthony, Trang"
date: "3/18/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

## Formula and Basics

## Loading required R packages

```{r}
library("readxl")
library("tidyverse")
library("flexplot")
```


## Data description

```{r}
titanic <- read_excel("Titanic.xlsx")
titanic
```


## Examples of data and problem

## Visualization

This the bi-variate dependency result.

```{r}
a = flexplot(Name~1, data = titanic)
b = flexplot(PClass~1, data = titanic)
c = flexplot(Age~1, data = titanic)
d = flexplot(Sex~1, data = titanic)
e = flexplot(Survived~1, data = titanic)
require(cowplot)
plot_grid(a, b, c, d, e, nrow=2)
```


## Analysis

Let us look at the multivariate dependency result.

```{r}
f = flexplot(Survived~Sex | Age + PClass, data = titanic, method="Binomial", se=F, jitter=c(0, 0.2)) 
plot_grid(f)
```


```{r}
f = flexplot(Survived~Age, data = titanic, method="Binomial", se=F, jitter=c(0, 0.1))
g = flexplot(Survived~Sex, data = titanic, method="Binomial", se=F, jitter=c(0, 0.2))
h = flexplot(Survived~PClass, data = titanic, method="Binomial", se=F, jitter=c(0, 0.2))
plot_grid(f, g, h)
```


## Computation

## Interpretation

## Model evaluation

## Regression line

## Model assessment

## Model summary

## Coefficients significance Prediction and Model accuracy

## Conclusion 

## Summary

## Reference
